### 2009-01-05 articles/2009/geoinformatics/article.tex
started with the article
git-svn-id: https://svn.osgeo.org/qgis/trunk@9926 c8812cc2-4d05-0410-92ff-de0c093fc19c

\section{Section}
\pagenumbering{arabic}
\setcounter{page}{1}

Einen guten Forscher erkennt man daran, dass er alle Hintergruende erforscht.
Ich, Prof. Lactosius, bin natuerlich ein guter Forscher. Deshalb habe ich auch
die Quelle der Schulmilch, die Kuehe, gruendlich erforscht.

\subsection{Subsection}

Ich weiss schon, was ihr jetzt sagen werdet. Jeder weiss, wie eine Kuh aussieht.
Aber auch bei den Kuehen habe ich kleine und groessere Unterschiede entdeckt.
Also los, folgt mir ins Land der Kuehe.

\begin{figure}[h]
   \begin{center}
   \caption{Example Figure}\label{fig:example-figure}\smallskip
   \includegraphics[clip=true]{test-image}
\end{center}
\end{figure}

\minisec{Minisec}

...

>>>>

\section{Quantum GIS 1.0.0}
\pagenumbering{arabic}
\setcounter{page}{1}

Quantum GIS (QGIS) is a cross-platform (GNU/Linux, MS Windows, Mac OSX) open
source application with a growing number of common GIS features and
functions. QGIS is licensed under the GNU General Public License and an
official member project of the Open Source Geospatial Foundation (OSGeo). The
current official version is 1.0.0, aka "Kore" and was released on January 05,
2009.

\subsection{History}

The idea for Quantum GIS was born in the beginning of 2002 when Gary Sherman
began looking for a GIS viewer for Linux that was fast and supported a wide
range of data stores. That, coupled with an interest in coding a GIS
application led to the creation of the project. In the beginning Quantum GIS
was established as a project on SourceForge in June 2002 with the first,
mostly non-functioning release on July 19, 2002. This first release supported
only PostGIS layers.

Within the last 7 years, the project

\subsection{QGIS Community}

\begin{figure}[h]
   \begin{center}
   \caption{QGIS Community Map}\label{fig:community-map}\smallskip
   \includegraphics[clip=true]{community-map}
\end{center}
\end{figure}

\subsection{Functionality}

\subsection{Development}

\subsection{Conclusion}

\minisec{Authors}

The authors of this article are QGIS Project Steering Committee Members:

Otto Dassau <dassau@nature-consult.de>  
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfinity.com>
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>
\\Paolo Cavallini <cavallini@faunalia.it>

\minisec{Links}

For more information, have a look at the following website:

Quantum GIS website: http://qgis.osgeo.org
